The SMT Competition 2015--2018

### 2019-08-16 2018/report/SMT-COMP.tex
has relatively few -> has few
a benchmarks -> a benchmark

Solvers that rank in high position in the competition-wide ranking
(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
but there are exceptions.  For instance, SMTInterpol has relatively
few unique solutions, despite achieving third place in the
competition-wide ranking in~2017 and~2018.  However, almost every
(sound) solver in the competition solves at least some benchmarks
uniquely, and hence contributes to the state-of-the-art.

@@

We only consider the \maintrack here, which contains a mixture of problems that
are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable
and unknown status benchmarks per division and year is given in
Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
less meaningful since a benchmarks usually contains a multitude of both
satisfiable and unsatisfiable incremental queries
(which may depend on each other).
For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
are used, which renders this analysis useless for this track.

>>>>

Solvers that rank in high position in the competition-wide ranking
(Section~\ref{sec:floc}) often also solve many benchmarks uniquely,
but there are exceptions.  For instance, SMTInterpol has few unique
solutions, despite achieving third place in the competition-wide
ranking in~2017 and~2018.  However, almost every (sound) solver in the
competition solves at least some benchmarks uniquely, and hence
contributes to the state-of-the-art.

@@

We only consider the \maintrack here, which contains a mixture of problems that
are satisfiable and unsatisfiable. A percentage of satisfiable, unsatisfiable
and unknown status benchmarks per division and year is given in
Table~\ref{table:benchmarks-main-track}.  For the \apptrack, this analysis is
less meaningful since a benchmark usually contains a multitude of both
satisfiable and unsatisfiable incremental queries
(which may depend on each other).
For the \ucoretrack, only known unsatisfiable benchmarks from the \maintrack
are used, which renders this analysis useless for this track.
